### 2018-03-17 Sections/essay_security_implications_of_the_global_quantum_internet.tex
Trump tweet

Combined with encrypted quantum computing protocols\index{Encrypted quantum computation}, no one would even know what they were up to when using this awesome computing power, and what they learn, they could keep to themselves. Alg.~\ref{alg:russian} describes a typical protocol for a particularly nefarious application for this.

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function MakeAmericaGreatAgain(Putin):
\begin{enumerate}
    \item A Russian bedroom hacker with no direct access to quantum technology, delegates a factorisation algorithm to the cloud using homomorphic encryption.
    \item The computation is physically executed on a server in the United States.
    \item The result is returned to our Russian comrade.
    \item The Russian uses the obtained private RSA key to hack Hillary's emails.
    \item The emails are strategically leaked during the next Presidential election.
    \item This swings the election in favour of Trump\texttrademark.
    \item The NSA and FBI have no clue who was behind it, since it was homomorphically encrypted.
    \item They blame Edward Snowden.
    \item Fox News\texttrademark \,calls for his execution.
    \item They'd kick themselves if they found out the algorithm was actually executed on US soil.
    \item Unless the NSA switches off the entire quantum internet, they can't prevent it from happening again in subsequent elections.
    \item return(America is Great Again\texttrademark).
    \item $\Box$
\end{enumerate}}}}
\caption{A typical example of a nefarious use for cloud quantum computation.} \label{alg:russian}\index{Trump}
\end{table}

@@

>>>>

Combined with encrypted quantum computing protocols\index{Encrypted quantum computation}, no one would even know what they were up to when using this awesome computing power, and what they learn, they could keep to themselves. Alg.~\ref{alg:russian} describes a typical protocol for a particularly nefarious application for this, with the end result shown in Fig.~\ref{fig:trump_tweet}.

\renewcommand{\tablename}{ALG.}

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function MakeAmericaGreatAgain(Putin):
\begin{enumerate}
    \item A Russian bedroom hacker with no direct access to quantum technology, delegates a factorisation algorithm to the cloud using homomorphic encryption.
    \item The computation is physically executed on a server in the United States.
    \item The result is returned to our Russian comrade.
    \item The Russian uses the obtained private RSA key to hack Hillary's emails.
    \item The emails are strategically leaked during the next Presidential election.
    \item This swings the election in favour of Trump\texttrademark.
    \item The NSA and FBI have no clue who was behind it, since it was homomorphically encrypted.
    \item They blame Edward Snowden.
    \item Fox News\texttrademark \,calls for his execution.
    \item They'd kick themselves if they found out the algorithm was actually executed on US soil.
    \item Unless the NSA switches off the entire quantum internet, they can't prevent it from happening again in subsequent elections.
    \item return(America is Great Again\texttrademark).
    \item $\Box$
\end{enumerate}}}}
\caption{A typical example of a nefarious use for cloud quantum computation. See Fig.~\ref{fig:trump_tweet} for the outcome.} \label{alg:russian}\index{Trump}\index{Covfefe}
\end{table}

@@

\begin{figure}[!htb]
\includegraphics[width=0.47\textwidth]{trump_tweet}
\caption{The Presidential response to Alg.~\ref{alg:russian}.}\label{fig:trump_tweet}\index{Trump}\index{Sad}\index{Covfefe}
\end{figure}
